A Framework for Classification of Social Machines

### 2013-02-09 latex/sig-alternate.tex
added basic paper structure
including bullet points for sections 1 and 2. examples need to be
further discussed

Sociam machines classification.

>>>>

What are social machines and why are they important

An emerging, interdisciplinary field of research and development with a growing number of social machine instances and studies about them

We propose a classification framework for social machines. Targeted audiences

* research community: shared terminology, set of key features and their possible instantiations based on the analysis of a relevant set of 50 (?) social machines (both popular systems as well as long tail systems); facilitates the study of design and evolution patterns; supports research on how communities emerge and develop and organizational studies (mechanism design, incentives); different research approaches can be better compared and aligned.

* developer community: provides a theoretical grounding for the realization of new systems, informs system design and operation (what features should be implemented, what features are more important than others); enables predictions on user behavior and community development.

The framework is based on interviews with XXX researchers covering XXX systems and was preliminary evaluated with respect to ...

\section{Methodology}

How was the classification framework defined

* interviews with XXX researchers on key descriptive features of systems they are familiar with

* consolidation of features listed for a resulting set of 50 (?) social machines

* grid analysis to identify groups of similar systems

* evaluation with respect to correctness, completeness, clarity, extendability in user survey, additional data set of XXX systems

\section{Classification framework}

First explain main principles: Distinction between application system and enabling technology; contributions, actions, activities, purpose, etc

\section{Usage examples}
Wikipedia

GalaxyZoo (?)

Ushahidi

Facebook

MechanicalTurk

GWAPs

\section{Related work}

existing classification systems in CSCW, collective intelligence, social computing systems

\section{Conclusions and future work}

Detail evaluation plans

Feedback from different disciplines, and from the developers community
